Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
added two software diagram figures, and the photo of the pantilt

\documentclass[10pt,twocolumns]{report}
\usepackage[pdftex]{graphicx}
\usepackage[left=1.5in, right=1.5in, top=1.25in, bottom=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=blue
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\newcommand{\degrees}[1]
{
\begin{math}
#1^{\circ} 
\end{math}
}
\hyphenation{auto-nomous construction}

@@

\subsection{Hardware}
Single board computer: beagleboard.

Description of each input, output interface.

Figure goes here: Hardware connection diagram. PAT
\subsection{Software}
\label{sec:autopilot_software}
PAT

Figure goes here: interprocess communication. PAT
\subsection{Ground Station}
Because we based our autopilot software on the Paparazzi project, we were able to make use of their excellent ground control software (GCS) with essentially no modifications.

@@

Each still picture is 5 megapixels, with an actual resolution of 2592 x 1944.  To determine how the images will appear from different altitudes, we have a table that maps the size of features in the world to pixels in our images at different altitudes.  We also see how this mapping will be affected when the camera is pointed straight down compared to when it is tilted at a 45 degree angle.  We can see that at 100 ft. each pixel will represent a little over $1/3$ of an inch when looking straight down, which should be a sufficient level of detail to accurately identify any target.  However, at 500 ft. each pixel is 2 inches wide when looking straight down, which will lead to blurry images.  We are confident that this level of detail will be enough to identify the shapes and colors of all targets at any required altitude, but we may have some difficulty identifying alpha-numerics on very small targets at high altitudes.  As a first year team, we feel that this is an acceptable level of detail.

\begin{tabular}{ccc}
{\bf altitude (ft)} & {\bf pixel width at $0,^{\circ}$ (in)} & {\bf pixel width at $45,^{\circ}$ (in)} \\
       100 &       0.38 &       0.54 \\
       200 &       0.76 &       1.08 \\
       300 &       1.14 &       1.62 \\
       400 &       1.52 &       2.16 \\
       500 &       1.90 &       2.69 \\
\end{tabular}

@@

\begin{figure}
	\centering
	\subfloat[Isometric View]{\label{fig:pantilt_isometric} 
			\includegraphics[width=0.75\textwidth]{../images/pantilt_isometric.png}}
\\
	\subfloat[Side View.]{\label{fig:pantilt_side} 
			\includegraphics[width=0.75\textwidth]{../images/pantilt_side.png}}
	\caption{Pan Tilt Unit}
	\label{fig:pantilt}
\end{figure}
\begin{figure}
	\subfloat[Linkage Detail View]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.6\textwidth]{../images/pantilt_linkdetail.png}}
	\subfloat[Linkage Velocity Plots]{\label{fig:pantilt_linkplots} 
			\includegraphics[width=0.4\textwidth]{../images/pantilt_linkplot.png}}
	\caption{Tilt Linkage Detail}
	\label{fig:pantilt_link}
\end{figure}

@@

The total height of the imaging system is 8.75", only 4'' of which is exposed below the fuselage of the aircraft. The rotating assembly is, on its widest dimension 2.13", and would fit inside a 2.5" cylinder. Wires exiting the side of the camera, inside the fuselage, may make the assembly a bit wider. Because the maximum rotation is only \degrees{1260}, the camera and tilt servo wires only have to be capable of wrapping \degrees{\pm 630} around the shaft below the thrust bearing. A wire guide will be added to keep the wires from tangling once construction of the pan-tilt is complete and installed in the aircraft.

>>>>

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage[left=1.5in, right=1.5in, top=1.25in, bottom=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=blue
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\itemspace}{	\setlength{\itemsep}{0cm} \setlength{\parskip}{0cm}}
\newcommand{\degrees}[1]
{
\begin{math}
#1^{\circ} 
\end{math}
}
\hyphenation{auto-nomous construction}

@@

\subsection{Hardware}
Description of components selected.
Description of each input, output interface.
\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{../images/hardware_conn_diagram.pdf}
	\caption{Hardware connection diagram for the autopilot and imaging systems. Only one of the 9 axis AHRS and Thermopile Attitude Sensor are used.}
	\label{fig:hardware_conn_diagram}
\end{figure}

\subsection{Software}
\label{sec:autopilot_software}

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{../images/software_comm_diagram.pdf}
	\caption{Communications diagram}	
	\label{fig:software_comm_diagram}
\end{figure}

\subsection{Ground Station}
Because we based our autopilot software on the Paparazzi project, we were able to make use of their excellent ground control software (GCS) with essentially no modifications.

@@

Each still picture is 5 megapixels, with an actual resolution of 2592 x 1944.  To determine how the images will appear from different altitudes, we have a table that maps the size of features in the world to pixels in our images at different altitudes.  We also see how this mapping will be affected when the camera is pointed straight down compared to when it is tilted at a 45 degree angle.  We can see that at 100 ft. each pixel will represent a little over $1/3$ of an inch when looking straight down, which should be a sufficient level of detail to accurately identify any target.  However, at 500 ft. each pixel is 2 inches wide when looking straight down, which will lead to blurry images.  We are confident that this level of detail will be enough to identify the shapes and colors of all targets at any required altitude, but we may have some difficulty identifying alpha-numerics on very small targets at high altitudes.  As a first year team, we feel that meeting the ``threshold'' rather than the ``objective'' goals, at the edge of the altitude envelope, is an acceptable level of performance.

\begin{tabular}{ccc}
\\{\bf altitude (ft)} & {\bf pixel width at $0,^{\circ}$ (in)} & {\bf pixel width at $45,^{\circ}$ (in)} \\
       100 &       0.38 &       0.54 \\
       200 &       0.76 &       1.08 \\
       300 &       1.14 &       1.62 \\
       400 &       1.52 &       2.16 \\
       500 &       1.90 &       2.69 \\
\end{tabular}

@@

\begin{figure}
	\centering
	\subfloat[Isometric View]{\label{fig:pantilt_isometric} 
			\includegraphics[width=0.45\textwidth]{../images/pantilt_isometric.png}}
	\subfloat[Side View.]{\label{fig:pantilt_side} 
			\includegraphics[width=0.45\textwidth]{../images/pantilt_side.png}}
\\
	\subfloat[Photograph of pan tilt unit installed in \emph{Daedalus}]{\label{fig:pantilt_photo}
			\includegraphics[width=0.75\textwidth]{../images/pantilt_photo1.jpg}}
	\caption{Pan Tilt Unit}
	\label{fig:pantilt}
\end{figure}
\begin{figure}
	\subfloat[Linkage Detail View]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.6\textwidth]{../images/pantilt_linkdetail.png}}
	\subfloat[Linkage Velocity Plots]{\label{fig:pantilt_linkplots} 
			\includegraphics[width=0.4\textwidth]{../images/pantilt_linkplot.png}}
	\caption{Tilt Linkage Detail}
	\label{fig:pantilt_link}
\end{figure}

@@

The total height of the imaging system is 6.75", a maximum 2'' of which is exposed below the fuselage of the aircraft. The rotating assembly is, on its widest dimension 2.13", and would fit inside a 2.5" cylinder. Wires exiting the side of the camera, inside the fuselage, may make the assembly a bit wider. Because the maximum rotation is only \degrees{1260}, the camera and tilt servo wires only have to be capable of wrapping \degrees{\pm 630} around the shaft below the thrust bearing. A wire guide will be added to keep the wires from tangling once construction of the pan-tilt is complete and installed in the aircraft.
